---
title: "telraamR"
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This package provides wrappers for Telraam API calls

## Instalation

For the instalation you need to have the \`remotes\`\` library.

```{r,eval=FALSE}
install.packages("remotes")
```

Once `remotes` is available. The package can be installed using the following code:

```{r,eval=FALSE}
remotes::install_github("juanfonsecaLS1/telraamR")
```

To load the package:

```{r}
library(telraamR)
```


## Set the Authentintication token

An authentication token is needed for using the Telraam API. If you do not have one, you can obtain one by registering in Telraam [here](https://www.telraam.net/en/register). Once you have obtained the token, it can be set using the following line of code:

```{r,eval=F}
usethis::edit_r_environ()
```

Save your token into the `.Renviron` file that is opened when you execute the command above and restart your session.
You can check to see if the token has been loaded as follows:

```{r,eval=F}
Sys.getenv("telraam")
```


The authentication token can also be provided in the `mytoken` argument of functions that call the Telraam API.

## Usage

### Cameras

It is possible to obtain all camera instances registered on the server with the following code:

```{r}
cameras_summary = read_telraam_cameras()

cameras_summary |> str()
```


### Traffic data

The hourly report for a single site can be obtained using the `read_Telraam_traffic` function. The following code shows an example of the use:

```{r}
data = read_telraam_traffic(9000003890,
                            time_start = "2023-03-25 07:00:00",
                            time_end = "2023-04-14 07:00:00",
                            report = "per-hour",
                            include_speed = FALSE)
```

The function returns a data set with the hourly traffic by vehicle type and direction

```{r}
data |>
  str()
```


If the `include_speed` is set as `TRUE`. The returned data frame will include the binned speed distribution for cars

```{r,results='hide',warning=FALSE}
library(tidyverse)
```


```{r}
data = read_telraam_traffic(9000003890,
                            time_start = "2023-03-25 07:00:00",
                            time_end = "2023-04-10 07:00:00",
                            report = "per-hour",
                            include_speed = TRUE)

data |>
  select(date,starts_with("car speed")) |>
  str()
```

### Segments Location

```{r}
segments = read_telraam_segments()
```

```{r}
library(tmap)
tmap_mode("view")

tm_shape(segments)+tm_lines()
```


